Towards Transparency and Open Science

### 2023-02-15 manuscript.Rmd
personal to generic

Information theory provides a rigorous mathematical measure that can be understood as the verisimilitude of a theory [@niiniluotoVerisimilitudeThirdPeriod1998].
The distance to the truth can be formalized in terms of how much information about the truth is lost when the theory is used to model reality [@rosenkrantzMeasuringTruthlikeness1980].
Expressed mathematically, assume the existence of a function $f(x)$ that yields the likelihood of observing the state of the world $x$ where $f$ represents the ground truth.
When interested in how much information is lost when using $g(x)$, our theory, instead of $f(x)$, the reality, over all possible states $\mathcal{X}$.
Expressed as lost bits of information, a measure known as Kullback–Leibler divergence [@kullbackInformationSufficiency1951], this results:
<!--x is a single state, X is the random variable, and \mathcal{X} is all possible outcomes of X-->
\begin{align} 
\mathcal{L}_{KL}(f, g) &=\int_{\mathcal{X}}f(x)\log\left(f(x)\right)\mathrm{d}x - \int_{\mathcal{X}}f(x)\log\left(g(x)\right)\mathrm{d}x\\
&= \mathbb{E}_{X \sim f}\left[\log(f(x))\right] - \mathbb{E}_{X \sim f}\left[\log(g(x))\right]\label{eq:klexp}
\end{align}

>>>>

Information theory provides a rigorous mathematical measure that can be understood as the verisimilitude of a theory [@niiniluotoVerisimilitudeThirdPeriod1998].
The distance to the truth can be formalized in terms of how much information about the truth is lost when the theory is used to model reality [@rosenkrantzMeasuringTruthlikeness1980].
Expressed mathematically, assume the existence of a function $f(x)$ that yields the likelihood of observing the state of the world $x$ where $f$ represents the ground truth.
When interested in how much information is lost when using $g(x)$, the theory, instead of $f(x)$, the reality, over all possible states $\mathcal{X}$.
Expressed as lost bits of information, a measure known as Kullback–Leibler divergence [@kullbackInformationSufficiency1951], this results:
<!--x is a single state, X is the random variable, and \mathcal{X} is all possible outcomes of X-->
\begin{align} 
\mathcal{L}_{KL}(f, g) &=\int_{\mathcal{X}}f(x)\log\left(f(x)\right)\mathrm{d}x - \int_{\mathcal{X}}f(x)\log\left(g(x)\right)\mathrm{d}x\\
&= \mathbb{E}_{X \sim f}\left[\log(f(x))\right] - \mathbb{E}_{X \sim f}\left[\log(g(x))\right]\label{eq:klexp}
\end{align}
